Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-14 paper/main.tex
added a new panel to figure 9, showing how fingerprints become more stable on "stabilize" and "random" lists, and less stable on "destabilize" lists

        \caption{\textbf{Adaptive free recall.} \textbf{A.} Average probability
        of recall (taken across words, lists, and participants) for lists from
        each adaptive condition. \textbf{B.} Average temporal clustering scores
        for lists from each adaptive condition. \textbf{C.} Recall probability
        versus temporal clustering scores by participant (main panel; each
        participant contributes one dot per condition) and averaged within
        condition (inset; each dot represents a single condition). All panels:
        Error bars and ribbons denote bootstrap-estimated 95\% confidence
        intervals. For additional details about participants' behavior and
        performance during the adaptive conditions, see
        Figure~\dynamicsAdaptive.}

@@

Overall, we found that participants tended to be better at remembering words on
stabilize lists relative to words on random ($t(59) = 1.740, p = 0.087$) or
destabilize ($t(59) = 1.714, p = 0.092$) lists (Fig.~\ref{fig:adaptive}A).
Participants showed no reliable differences in their memory performance on
destabilize versus random lists ($t(59) = -0.249, p = 0.804$). Participants
also exhibited stronger temporal clustering on stabilize lists, relative to
random ($t(59) = 3.554, p = 0.001$) and destabilize ($t(59) = 4.045, p <
0.001$) lists (Fig.~\ref{fig:adaptive}B). We found no reliable differences in
temporal clustering for items on random versus destabilize lists ($t(59) =
-0.781, p = 0.438$).

>>>>

        \caption{\textbf{Adaptive free recall.} \textbf{A.} Average probability
        of recall (taken across words, lists, and participants) for lists from
        each adaptive condition. \textbf{B.} Average temporal clustering scores
        for lists from each adaptive condition. \textbf{C.} Recall probability
        versus temporal clustering scores by participant (main panel; each
        participant contributes one dot per condition) and averaged within
        condition (inset; each dot represents a single condition). \textbf{D.}
        Per-list correlations between the current list's fingerprint and the
        average fingerprint computed from all previous lists. The normalized
        list numbers ($x$-axis) denote the number of lists of the same type
        that the participant had experienced at the time of the current list.
        All panels: Colors denote the sorting type (condition) for each list.
        Error bars and ribbons denote bootstrap-estimated 95\% confidence
        intervals. For additional details about participants' behavior and
        performance during the adaptive conditions, see
        Figure~\dynamicsAdaptive.}

@@

Participants' fingerprints on stabilize and random lists tended to become
(numerically) slightly more similar to their average fingerprints computed from the
previous lists they had experienced, and their fingerprints on destabilize
lists tended to become numerically less similar (Fig.~\ref{fig:adaptive}D).
Overall, we found that participants tended to be better at remembering words on
stabilize lists relative to words on random ($t(59) = 1.740, p = 0.087$) or
destabilize ($t(59) = 1.714, p = 0.092$) lists (Fig.~\ref{fig:adaptive}A).
Participants showed no reliable differences in their memory performance on
destabilize versus random lists ($t(59) = -0.249, p = 0.804$). Participants
also exhibited stronger temporal clustering on stabilize lists, relative to
random ($t(59) = 3.554, p = 0.001$) and destabilize ($t(59) = 4.045, p <
0.001$) lists (Fig.~\ref{fig:adaptive}B). We found no reliable differences in
temporal clustering for items on random versus destabilize lists ($t(59) =
-0.781, p = 0.438$).
